\documentclass[11pt]{article}
\usepackage[vcentering, dvips, papersize={8.5in,11in}, tmargin=1in,lmargin=0.5in,rmargin=0.7in]{geometry}
\usepackage{fancyhdr}

% -------------
% Margin Setup
% -------------

%\setlength{\paperwidth}{8.5in}
%\setlength{\paperheight}{11in}
%\setlength{\headsep}{3pt}

% \parindent: indentation of paragraphs
\setlength{\parindent}{0pt}
% \parskip: gap between paragraphs
%\setlength{\parskip}{3pt}

\setlength{\headheight}{43pt}
% \itemsep: space between successive items.
%\setlength{\itemsep}{0pt}
% \topsep: space between first item and preceding paragraph.
%\setlength{\topsep}{3pt}
% \partopsep: extra space added to \topsep when environment starts a new paragraph.
%\setlength{\partopsep}{0pt}

\pagestyle{fancyplain}

%\setlength{\tabcolsep}{0in}
% -------------

% -------------
% Custom commands

\newcommand{\resheading}[1]{\vspace{1pt}\textbf{#1}}

\newcommand{\ressubheading}[4]{\vspace{6pt}
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{#1} --- & #3, #2, \textit{#4} \\
\end{tabular*}}

\newcommand{\ressubsubheading}[1]{\vspace{6pt}#1}

\newcommand{\resitem}[1]{\item #1}

\newcommand{\resawarditem}[2]{\item #1 \hfill \textit{#2}}

\newcommand{\ressep}{\vspace{6pt}\hrule\vspace{3pt}}

\lhead[]{\textbf{701 Baltic Circle, Unit 721\\Redwood City, CA 94065, USA}}
\rhead[]{\huge{\textbf{Andrew Y. Yao}}\\\small{andrewyao@gmail.com, (650) 269 8522}\\ http://www.linkedin.com/in/andrewyao}

\begin{document}

\resheading{SUMMARY}

A software engineer with \textbf{nine} years of development experience; a passionate, resourceful problem-solver.
\ressep{}

\resheading{PROGRAMMING SKILLS}

\begin{itemize}
\resitem{\textbf{Extensive Experience} in \\
	\textbf{Front End}: AJAX, JavaScript, JQuery, CSS, Flex, UI Automation.\\
	\textbf{Back End}: C/C++ (COM, ATL), Java, Oracle Database, SQL, PL/SQL. Test Driven Development.}
\resitem{\textbf{Environment}: Eclipse, Visual Studio, Linux, Windows, Mac, VMs.}
\resitem{\textbf{Working Knowledge} in \LaTeX, Apache, Python, Perl, PHP, MySQL, RESTful architecture.}
\end{itemize}

\ressep{}
\resheading{EXPERIENCE}

\ressubheading{Principal Member of Technical Staff}{Redwood Shores, CA}{Oracle USA}{6/2004 - Present}

\ressubsubheading{\textbf{Technical Lead} in Oracle Support portal, used by millions of Oracle DBAs worldwide.
One of the projects was highlighted in \textbf{Oracle Open World 2009, CEO Larry Ellison's keynote}.}

\begin{itemize}
\resitem{\textbf{Modularized and Refactored} 300K front-end code into 22 separate, layered libraries.}
\resitem{\textbf{Re-architected} the front-end into dynamically loadable modules. Reduced initial payload by 40\%.}
\resitem{\textbf{Improved} developer productivity; significantly reduced the client-side compilation time from 3 minutes down to 30 seconds using module techniques; reduced the server-side compilation + deployment + test time from 5+ minutes down to seconds using JUnit.}
\resitem{\textbf{Implemented} multi-threaded back-end web services, caching, and proxy to external web services.}
\resitem{\textbf{Promoted} best practices for writing testable code. Improved code coverage from nothing to 60\%.}
\resitem{The \textbf{`Go to guy'} for Flex, JavaScript, and all other framework related questions.}
\end{itemize}

\ressubsubheading{\textbf{Technical Lead} in Monitoring Tools Development. Availability and performance monitoring across multiple geographical locations; used by internal and external customers; one of the larger contracts was in 7 digits. 
Acting as the architect, designed and developed the following key subsystems:}
\begin{itemize}
\resitem{A browser-plugin (C++ and JavaScript) that \textbf{records}, \textbf{analyzes}, and \textbf{replays} web transactions.}
\resitem{The browser-plugin part of a \textbf{tracing and diagnostic tool}, which shows the break down of time taken for HTTP requests, Java method calls, and SQLs in an interactive user session.}
\resitem{Many heuristic techniques that improve the recording accuracy: HTTP traffic and DOM correlation; dynamic variable detection; dynamic Regular Expression generation and substitution.}
\resitem{Clever event listening techniques that make the recording overhead negligable.}
\resitem{Parts of a URL fetching tool in C and Java, the key to monitoring availability and performance from multiple geographical locations, without using a real browser.}
\resitem{Over 30 complex JSP pages for services, web transaction, metrics and thresholds configuration.}
\resitem{Business model layer, persistence layer using Java, JDBC, SQL and PL/SQL. Tuned the performance of complex back-end SQL queries.}
\end{itemize}

\newpage

\ressubheading{Associate}{New York, NY}{Goldman Sachs Inc}{6/2001 - 8/2003}
\begin{itemize}
\resitem{\textbf{Consistently ranked} in the \textbf{top quartile} in the $360^{\circ}$ Annual Review System.}
\resitem{\textbf{Designed} reusable UI components for an in-house AJAX style web application framework.}
\resitem{\textbf{Significantly improved} the performance of the UI framework and UI components.}
\resitem{\textbf{Developed} a distributed n-tier document search and retrieval system.}
\resitem{\textbf{Developed} Excel-based financial models, risk analysis models, and staffing management solutions.}
\resitem{\textbf{Maintained} infrastructure scripts and database schema that manage thousand of desktop machines and
servers around the globe.}
\resitem{The \textbf{`Go to guy'} for JavaScript, CSS, and Excel questions.}
\end{itemize}

\ressubheading{Intern Research Engineer}{Australia}{Canon Information Systems Research}{12/1998 - 2/2000}
\begin{itemize}
\resitem{\textbf{Researched} two-dimensional image demodulation algorithms, and made a considerable intellectual contribution to the algorithm using spatial and Fourier based methods and MATLAB.}
\resitem{\textbf{Developed} parts of a successful, robust, and reliable scientific image analysis application using C/C++.}
\end{itemize}

\ressep{}
\resheading{EDUCATION}

\ressubheading{M.S., Computer Science, Full Tuition Scholarship, GPA 3.9}{Ithaca, NY}{Cornell University}{2004}
\begin{itemize}
\resitem{\textbf{Thesis}: Quark - A next-generation data management system that searches heterogeneous data source using XQuery. Part of a team that built a functional, end-to-end, \textbf{open source} XQuery engine in C++.}
\resitem{Database Implementation, Graphics, Distributed Systems, Networks, Scientific Computing}

\end{itemize}

\ressubheading{B.S., Computer Engineering, GPA 3.8 - 3.9}{Australia}{University of New South Wales}{2000}
\begin{itemize}
\resitem{\textbf{First Class Honors}, \textbf{Rank}: $2^{nd}/111$ students,
Thesis Scholarship, Canon Academic Excellence Awards}
\resitem{\textbf{Thesis}: A video annotation and search tool that allows users to annotate (tag) semantic information (keywords) on video clips, and search video clips using the keywords.}
\resitem{\textbf{Teaching Assistant}: Functional Programming, Algorithms}
\resitem{\textbf{Research Assistant}: Developed the back-end of an open source search engine \textbf{CVSSearch} using data mining and advanced string matching techniques.}
\resitem{\textbf{Published} in IEEE International Conference on Software Maintenance (ICSM 2001), Pages 364 - 373.}
\resitem{Algorithms, Operating System, OO Design, Database, Computer Architecture, Neural Networks, Image Processing, etc}
\end{itemize}

\ressep{}
\resheading{OTHER AWARDS}

\begin{itemize}
\resawarditem{\textbf{Member} of Australian Mathematics Olympiad National Team Training Squad}{1995 \& 1996}
\resawarditem{Bronze \textbf{Medallist} in Asian Pacific Mathematics Olympiad}{1996}
\resawarditem{Gold \textbf{Medallist} in Australian Mathematics Olympiad}{1995 \& 1996}
\resawarditem{\textbf{Medallist} in Australian Westpac Mathematics Competition}{1991 \& 1995}
\end{itemize}

\end{document}
